\begin{abstractEN}

\setlength{\baselineskip}{1.5em} 
%Real-valued optimization is a famous
%problem which has been researched for several decades, and it is also
%applied to many real-world problems. To conquer the difficulty of
%infinity searching space , there are many approaches developed to solve
%the problem. For example, evolution strategies, real-coded genetic
%algorithm. Evolution strategy (ES) is an optimization technique based on
%ideas of evolution and self-adaptaion while covariance matrix adaptaion
%evolution strategy (CMA-ES) is probably best one of the ES family.
%Real-coded extended compact genetic algorithm (rECGA) is a branch of
%Estimation of Distribution Algorithms (EDAs) which replace traditional
%operators of genetic algorithm, crossover and mutation, with modeling
%and sampling. This thesis will give a brief introduction for both
%techniques. The illustrated method in this work is kind of domain
%discretion. CMA-ES performs well on exploitation, and we want to improve
%the ability of exploration. To achieve that, we design an algorithm
%using 2-layer CMA-ES to explore the information extracted from local
%optima.


Real-valued optimization is a famous, well studied problem that has been
applied to many real-world problems.
Many kinds of difficulties are investigated, such as a large search
space, dependencies among decision variables.
As a result, many approaches are developed to conquer the difficulties.
For example, evolution strategies and real-coded genetic algorithms.
Evolution strategy (ES) is an optimization technique based on ideas of
evolution and self-adaptaion while covariance matrix adaptaion evolution
strategy (CMA-ES) is probably best one of the ES family.
Real-coded extended compact genetic algorithm (rECGA) is a branch of
Estimation of Distribution Algorithms (EDAs) which replace traditional
operators of genetic algorithm, crossover and mutation, with modeling
and sampling.
This thesis will give a brief introduction for both techniques.

Inspired by both techniques, this work aims to propose an algorithm to
locate a more possible region where global optimum resides.
By combining CMA-ES, $k$-means clustering and MAB problems, we design an
algorithm using 2-layer CMA-ES to extract the implicit tendency formed
by local optima.
\\

\noindent
\textbf{Keywords} \\
\noindent
Real-valued optimization problem, black-box optimization, covariance matrix adaptation evolution
strategy, multi-armed bandit problem.

\end{abstractEN}
