\begin{acknowledgementsEN}

\noindent
%\textbf{Advisor}\\
%Tian-Li Yu\\
%\\
%\textbf{Colleagues in Taiwan Evolutionary Intelligence Lab} \\
%Yi-En Su\\
%Hsuan Lee, Chung-Hsiang Hsueh, Jen-Hao Chang,\\
%Po-Chun Hsu, Chung-Yu Shao, Chih-Yuan Chou, Wei-Ming Chen,\\
%Jie-Wei Wu, Shih-Ming Wang, Chu-Yu Hsu,\\
%Shih-Huan Hsu, Yu-Fan-Tung, Jia-Hui Wu,\\
%Chang-Yi Lyu, Chi-Yuang Tseng, Chia-Hua Chang\\
%\\
%\textbf{Writing Consultation} \\
%Ting-Chou Lin\\
%\\
%\textbf{The Thesis Committee} \\
%Yung-Yu Chuang, Ho-Lin Chen\\
%\\
%\textbf{My Family} \\
%\\
%\textbf{National Taiwan University} \\
%The basketball team of department of Computer Science and Information
%Engineering
%\\
%And lovely fianc\'{e} Ching-Hsuan Sandy Jao
First of all, I appreciate my advisor, Dr. Tian-Li Yu, the mose. Being
an advisor, Yu is always ready in his prefessional knowledge for
handling my problems in my research.
Besides, Yu is a kindly teacher that takes care of his students even in
daily life.
Without any improper stress, it is grateful to do research under the
advice of Yu.
Even I am not the most outstanding student of Yu's, I will always
be proud of being one of the members of Taiwan Evolutionary Intelligence
Laboratary.

Second, I give my credits to Yi-En Su and Ting-Chou Lin as my writing
consultation.
The two man major frustrated me when I am proud of my work and pointed
out the right way for me to finish this work.

Third, I would pay my gratefulness to the members of TEILab since 2010.
They are
Hsuan Lee, Chung-Hsiang Hsueh, Jen-Hao Chang,
Po-Chun Hsu, Chung-Yu Shao, Chih-Yuan Chou, Wei-Ming Chen,
Jie-Wei Wu, Shih-Ming Wang, Chu-Yu Hsu,
Shih-Huan Hsu, Yu-Fan-Tung, Jia-Hui Wu,
Chang-Yi Lyu, Chi-Yuang Tseng, Chia-Hua Chang.
With their company, I am introduced to the GA field, involved into the
lab and relaxed when I was preparing my work.

Furthermore, I really appreciate my teammates in NTU CSIE basketball
team, especially the ones in the group of `Tower of Saviors'.
Though without any direct help for this work, they always encouraged me
when I am depressed, and I would like to share this honor with these
guys.

I would like to appreciate my father, mother, brother and sister. Withot
their financial and mental support, it would be impossible for me to
finish this work.

Last but not least, I am going to give all my remain credits to my
fianc\'{e}, Ching-Hsuan Sandy Jao.
In the last stage of this work, she always encourged me when I tried to
give up, endured my bad temper, accompanied with me all day and night
and prepared for our wedding in December alone.
Without her support, I must had been crashed and given up doing this
work.

These people are all treasure of mine and will always kept in my mind
for life long.
I finished this work, grew up and faced the world with their assistance.
I love, respect them sincerely.
Thanks to the ones who are accidently involved into my life, and I hope
that I will one day also treasure of yours. 
\end{acknowledgementsEN}

