\chapter{Introduction} \label{ch:introduction}

With the rapid development of knowledge and technology, optimization
techniques have been widely applied to various fields, such as curve fitting
and parameter tuning.  Generally speaking, optimization is the process
of obtaining alternatives with higher performance. 
In this thesis, we focus on real-valued problem optimization, which
stands for minimizing or maximizing function values.

Real-world problems are usually considered as black-box problems.
This means we have no information about the internal structure of the
objective functions including analytic form, gradient, etc.
Under this unknown problem structure, we cannot generate the global
optimum through any mathematical approach.
As a result, stochastic algorithms are introduced to approximate the
global optimum.

Evolution strategy (ES)~\cite{Rechenberg:1973}~\cite{Rechenberg:1994} is derived from evolution algorithms and
commonly applied to black-box optimization problems in continuous
domain; covariance matrix adaptation evolution strategy
(CMA-ES)~\cite{Hansen:1996}~\cite{hansen2001ecj}~\cite{hansen2003ecj} is a
famous one of ES family.
Covariance matrix is adopted by CMA-ES for representing current
distribution and self-adapted in the end of each iteration.
The feature of CMA-ES is the adaptivity of the step size and the
distribution by which offspring are generated.
By adopting historical information, the step size and the distribution
can be adjusted accordingly.

Unfortunately, CMA-ES faces difficulty on problems of real-valued
problem optimization.
Due to several properties of black-box problem, multi-modality and
uncertainty for example, CMA-ES converges to local optima with high
probability.
For uni-modal problems, CMA-ES is famous for ability of
\emph{exploitation}, but this property makes CMA-ES easily mislead by
multi-modal problems.
In order to make CMA-ES more feasible on multi-modal problems, this
thesis made some modification on it.

Our work relied on the hypothesis which we can assume that there are
multiple local optima when solving a multi-modal problem.
Also, we assume that the information of the region where global optimum
resides is somehow hidden in the locations of local optima and can be
retrieved by proper methods.
According to the assumption, we evolve the population consisting of
local optima in order to fetch the hill where global optimum exists.
By applying this 2-layers CMA-ES procedure, the modified CMA-ES is
expected to improve the ability of exploration, and this is just what we
lay concentration on.

Here is the organization of the following chapters: in the next section,
definition and analysis of real-valued function optimization along with
test problems of our work are presented, approaches for real-valued
function optimization are introduced in Chapter~\ref{ch:real-valued
  function optimization}.
The background of this work is introduced in
Chapter~\ref{ch:Approaches-for-real-valued-problem}.
Our methodology and related work are introduced in
Chapter~\ref{ch:method}. Experiment settings and results are introduced
in Chapter~\ref{ch:experiment}.
My summary and conclusion are given in Chapter~\ref{ch:conclusion}. 

